Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-24 ICLR25/Paper_noProof.tex
clean up

In this paper, we studied the LP relaxation of the exact MILP encoding of ReLU-DNNs.
It allowed us to accurately assess when the relaxation of a node impacts very little 
the accuracy, and when it impacts the accuracy importantly, in which case representing it with a binary/integer variable is preferable. This allows us to select a small set of important neurons to encode as a binary variables, improving accuracy drastically. Our automated choice of opened neurons necessitates $>4$x less integer variables than previous proposals \cite{DivideAndSlide} for the same accuracy. Our empirical studies revealed that Hybrid MILP, can yield highly accurate results, verifying up to 40\% more images than the SOTA ($\alpha,\beta$-Crown, winner of the 4 last VNNComp), with the same runtime. 
The reason is that $\alpha,\beta$-Crown can scale to large easy DNNs, but does not scale to 
hard even small DNNs: it hits a complexity wall, similarly as other compeating solutions. This opens a lot of perspectives, among which: verifying efficiently other hard instances; certifying $\epsilon$-robustness of images for $\epsilon$ as large as possible; 
verifying global rather than local properties \cite{lipshitz}.

>>>>

In this paper, we studied the LP relaxation of the exact MILP encoding of ReLU-DNNs.
It allowed us to accurately assess when the relaxation of a node impacts very little 
the accuracy, and when it impacts the accuracy importantly, in which case representing it with a binary/integer variable is preferable. This allows us to select a small set of important neurons to encode as a binary variables, improving accuracy drastically. Our automated choice of opened neurons necessitates $>4$x less integer variables than previous proposals \cite{DivideAndSlide} for the same accuracy. Our empirical studies revealed that Hybrid MILP, can yield highly accurate results, verifying up to 40\% more images than the SOTA ($\alpha,\beta$-Crown, winner of the 4 last VNNComp), with the same runtime. 
The reason is that $\alpha,\beta$-Crown can scale to large easy DNNs, but does not scale to 
hard even small DNNs: it hits a complexity barrier, similarly as other compeating solutions. This opens a lot of perspectives, among which: verifying efficiently other hard instances; certifying $\epsilon$-robustness of images for $\epsilon$ as large as possible; 
verifying global rather than local properties \cite{lipshitz}.

### 2024-09-24 ICLR25/valabstraction.tex
clean up

%\definecolor{applegreen}{rgb}{0.55, 0.71, 0.0}

@@

		\node[circle, draw= black, thick, minimum width = 20,
		minimum height = 20] (input1) {$n_1$};

		\node[circle, draw= black, thick, minimum width = 20,
		minimum height = 20] (input2) at ($(input1) + (0,-1.5)$) {$n_2$};

@@

		\node[circle, draw= black, thick, minimum width = 20,
		minimum height = 20] (hidden1) at ($(input1) + (2.5,0)$) {$n_3$};
		\node[circle, draw= black, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$n_4$};

		\node[circle, draw= black, thick, minimum width = 20,
		minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$\hat{n}_3$};
		\node[circle, draw= black, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$\hat{n}_4$};

		\node[circle, draw= black, thick, minimum width = 20,
		minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$n_5$};
		\node[circle, draw= black, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$n_6$};

		% Output layer
		\node[circle, draw= black, thick, minimum width = 20,
		minimum height = 20] (output1) at ($(input1) + (10,0)$){$\hat{n}_5$};

		\node[circle, draw= black, thick, minimum width = 20,
		minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$\hat{n}_{6}$};

>>>>

\definecolor{applegreen}{rgb}{0.55, 0.71, 0.0}

@@

		\node[circle, draw= applegreen, thick, minimum width = 20,
		minimum height = 20] (input1) {$n_1$};

		\node[circle, draw= applegreen, thick, minimum width = 20,
		minimum height = 20] (input2) at ($(input1) + (0,-1.5)$) {$n_2$};

@@

		\node[circle, draw= blue, thick, minimum width = 20,
		minimum height = 20] (hidden1) at ($(input1) + (2.5,0)$) {$n_3$};
		\node[circle, draw= blue, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$n_4$};

		\node[circle, draw= blue, thick, minimum width = 20,
		minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$\hat{n}_3$};
		\node[circle, draw= blue, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$\hat{n}_4$};

		\node[circle, draw= red, thick, minimum width = 20,
		minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$n_5$};
		\node[circle, draw= blue, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$n_6$};

		% Output layer
		\node[circle, draw= blue, thick, minimum width = 20,
		minimum height = 20] (output1) at ($(input1) + (10,0)$){$\hat{n}_5$};

		\node[circle, draw= blue, thick, minimum width = 20,
		minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$\hat{n}_{6}$};
